### 2025-09-11 paper/sec/authoring-workflow.tex
[update] interpretation examples wf

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}{0.48\linewidth}
        \centering
        \includegraphics[width=\linewidth]{fig/entire-workflow}
        \caption{Workflow}
        \label{fig:architecture}
    \end{subfigure}\hfill
    \begin{subfigure}{0.48\linewidth}
        \centering
        \includegraphics[width=\linewidth]{fig/data-flow}
        \caption{Data flow}
        \label{fig:dataflow}
    \end{subfigure}
    \caption{AI-assisted authoring process: workflow (a) and data flow (b).}
    \label{fig:overall-architecture}
\end{figure}

@@

\subsection{Paragraph with generated expression}
\label{subsec:paragraph-with-generated-expression}
Figure \ref{fig:fluid-example-paragraph} shows the Fluid code of a Paragraph with the expression generated by the authoring assistant.
Figure \ref{fig:fluid-scigen} shows the Fluid code written for the scigen datasets and examples.
\begin{figure}[h]
    \small
    {\lstinputlisting[language=Fluid]{../website/authoring-assistant/fluid/1805.02474v1-10.fld}}
    \vspace{-0.5em}
    \caption{Fluid source code example Paragraph}
    \label{fig:fluid-example-paragraph}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{fig/entire-workflow}
    \caption{Workflow}\label{fig:architecture}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}{0.50\linewidth}
        \centering
        \includegraphics[width=\linewidth]{fig/data-flow-correct}
        \caption{Author Acceptance Dataflow}
        \label{fig:data-flow-correct}
    \end{subfigure}\hfill
    \begin{subfigure}{0.50\linewidth}
        \centering
        \includegraphics[width=\linewidth]{fig/data-flow-error}
        \caption{Author Rejection Dataflow}
        \label{fig:dataflow-error}
    \end{subfigure}
    \caption{Two workflows of the Interpretation Agent. In Fig. \ref{fig:data-flow-correct}, the author accepts the generated expression after verifying its correctness online. In Fig. \ref{fig:dataflow-error}, the author identifies an error (the expression mentions accuracy, while the article highlights timing) and rejects it.}
    \label{fig:overall-architecture}
\end{figure}

@@

\subsection{Paragraph with generated expression}
\label{subsec:paragraph-with-generated-expression}
Figure \ref{fig:fluid-example-paragraph} shows the Fluid code of a Paragraph with the expression generated by the authoring assistant.
Figure \ref{fig:fluid-scigen} shows the Fluid code written for the scigen datasets and examples.
%\begin{figure}[h]
%    \small
%    {\lstinputlisting[language=Fluid]{../website/authoring-assistant/fluid/1805.02474v1-10.fld}}
%    \vspace{-0.5em}
%    \caption{Fluid source code example Paragraph}
%    \label{fig:fluid-example-paragraph}
%\end{figure}
